Cluster Paper

### 2015-04-01 ms.tex
added figure for survey area

\section{THE HETDEX SURVEY}
\editorial{This should probably go into the introduction. I don't think we need a whole section on something that a bunch of papers have already talked about.}

>>>>

\section{THE HETDEX SURVEY}
\editorial{This should probably go into the introduction. I don't think we need a whole section on something that a bunch of papers have already talked about.}
\begin{figure} 
	\includegraphics[width=0.49\textwidth]{surveyArea.pdf} 
	\caption{A polar azimuthal equidistant projection of the southern sky showing the sky area (approximately a quarter of the sky) covered by the Aardvark Simulations. Concentric circles are lines of constant declination, 10 to $-80\degree$ in $10\degree$ increments. Radial lines are lines of constant right ascension. Opaqueness of the region indicates the overlap of catalog tiles (see text for details).} 
	\label{fig:survey area} 
\end{figure}
